# rice

<!-- quarto render -->

```{r}
#| label: setup
#| include: false

library(badger)
library(beepr)
library(groomr) # github.com/danielvartan/groomr
library(lubridate)
library(readr)
library(stringr)
```

<!-- badges: start -->
```{r}
#| echo: false
#| output: asis

library(badger)

cat(
  badger::badge_repostatus("wip"),
  # badger::badge_custom(
  #   "CoMSES Network",
  #   "Placeholder",
  #   "1284C5",
  #   "https://www.comses.net/"
  # ),
  # # badger::badge_custom(
  #   "OSF DOI",
  #   "10.17605/OSF.IO/EAPZU",
  #   "1284C5",
  #   "https://doi.org/10.17605/OSF.IO/EAPZU"
  # ),
  # badger::badge_custom(
  #   "fair--software.eu",
  #   "%E2%97%8F%20%20%E2%97%8F%20%20%E2%97%8B%20%20%E2%97%8F%20%20%E2%97%8B-",
  #   "orange",
  #   "https://fair-software.eu"
  # ),
  # paste0(
  #   "[![FAIR checklist badge](https://fairsoftwarechecklist.net/badge.svg)]",
  #   "(https://fairsoftwarechecklist.net/v0.2?f=21&a=32113&i=32001&r=123)"
  # ),
  # badger::badge_custom( # CII Best Practices
  #   "openssf%20best%20practices",
  #   "Placeholder",
  #   "orange",
  #   "https://bestpractices.coreinfrastructure.org/"
  # ),
  badger::badge_license(
    "MIT",
    "green",
    url = "https://choosealicense.com/licenses/mit/"
  ),
  badger::badge_custom(
    "Contributor%20Covenant",
    "2.1",
    "4baaaa",
    "CODE_OF_CONDUCT.md"
  )
)
```
<!-- badges: end -->

## Overview

`rice` is a NetLogo model designed to simulate and visualize how rice crops respond to different climate conditions. It aims to support the integration of food agents into agent-based models and improve the reproducibility of these simulations.

The model runs in paralel with the [`LogoClim`](https://github.com/sustentarea/logoclim) model, which provides climate data from [WorldClim 2.1](https://worldclim.org/).

## How to Cite

If you use this model in your research, please cite it to acknowledge the effort invested in its development and maintenance. Your citation helps support the ongoing improvement of the model.

To cite `rice` in publications please use the following format:

Vartanian, D., & Carvalho, A. M. (2025). *rice: A NetLogo model of rice crop responses to climate conditions* [Computer software, NetLogo model]. [https://doi.org/](https://doi.org/)

A BibTeX entry for LaTeX users is:

```latex
@Misc{vartanian2025,
  title = {rice: A NetLogo model of rice crop responses to climate conditions},
  author = {{Daniel Vartanian} and {Aline Martins de Carvalho}},
  year = {2025},
  doi = {https://doi.org/},
  note = {NetLogo model}
}
```

## How to Contribute

```{r}
#| echo: false
#| output: asis

cat(
  badger::badge_custom( # Contributor Covenant
    "Contributor%20Covenant",
    "2.1",
    "4baaaa",
    "CODE_OF_CONDUCT.md"
  )
)
```

Contributions are welcome! Whether it's reporting bugs, suggesting features, or improving documentation, your input is valuable.

[![](https://img.shields.io/static/v1?label=Sponsor&message=%E2%9D%A4&logo=GitHub&color=%23fe8e86)](https://github.com/sponsors/danielvartan)

You can also support the development of `rice` by becoming a sponsor. Click [here](https://github.com/sponsors/danielvartan) to make a donation. Please mention `rice` in your donation message.

## License

```{r}
#| echo: false
#| output: asis

cat(
  badger::badge_license(
    "MIT",
    "green",
    url = "https://choosealicense.com/licenses/mit/"
  )
)
```

`rice` code is licensed under the [MIT License](https://opensource.org/license/mit). This means you can use, modify, and distribute the code freely, as long as you include the original license and copyright notice in any copies or substantial portions of the software.

## Acknowledgments

```{r}
#| echo: false
#| output: asis

htmltools::tags$table(
  htmltools::tags$tr(
    htmltools::tags$td(
      htmltools::tags$br(),
      htmltools::tags$br(),
      htmltools::tags$p(
        htmltools::tags$a(
          htmltools::tags$img(
            src = "images/sustentarea-logo.svg",
            width = 125
          ),
          href = "https://www.fsp.usp.br/sustentarea/"
        ),
        align = "center"
      ),
      htmltools::tags$br(),
      width = "30%"
    ),
    htmltools::tags$td(
      htmltools::tags$p(
        htmltools::tags$code("LogoClim"),
        "was developed with support from the Research and ",
        "Extension Center ",
        htmltools::tags$a(
          "Sustentarea",
          href = "https://www.fsp.usp.br/sustentarea/"
        ),
        " at the University of São Paulo (",
        htmltools::tags$a(
          "USP",
          href = "https://www5.usp.br/",
          .noWS = "outside"
        ),
        ")."
      ),
      width = "70%"
    )
  )
) |>
  knitr::raw_html()

htmltools::tags$table(
  htmltools::tags$tr(
    htmltools::tags$td(
      htmltools::tags$br(),
      htmltools::tags$p(
        htmltools::tags$a(
          htmltools::tags$img(
            src = "images/cnpq-logo.svg",
            width = 150
          ),
          href = "https://www.gov.br/cnpq/"
        ),
        align = "center"
      ),
      htmltools::tags$br(),
      width = "30%"
    ),
    htmltools::tags$td(
      htmltools::tags$p(
        "This project was supported by the Conselho Nacional de ",
        "Desenvolvimento Científico e Tecnológico - Brazil (",
        htmltools::tags$a(
          "CNPq",
          href = "https://www.gov.br/cnpq/",
          .noWS = "outside"
        ),
        ")."
      ),
      width = "70%"
    )
  )
) |>
  knitr::raw_html()
```
